Compiling list of medications based on BNF codes for dementia/AD & palliative care drugs

### 2023-02-13 compile_medications_from_bnf.Rmd
added more testing code for BNF medicine compiling

```{r}
library(tidyverse)
library(readxl)  # for loading excel files
library(janitor)  # for cleaning data
library(knitr)  # for pretty tables in the report
library(docxtractr)  # for reading data from table in .docx file
```

@@

```{r}
# TODO: process this if needed?
medicines_list <- 
  extracted_table %>%
  clean_names() %>%
  mutate(
    chapter = as.integer(str_extract(drug_class_name, pattern = "(?<=Chapter )\\d+"))
  ) %>%
  filter(bnf_subsection!="") %>%
  fill(chapter, .direction = "down")
```

>>>>

```{r}
library(tidyverse)
library(readxl)  # for loading excel files
library(janitor)  # for cleaning data
library(knitr)  # for pretty tables in the report
library(docxtractr)  # for reading data from table in .docx file
library(fuzzyjoin)  # for regex merges
```

@@

```{r}
# TODO: process this if needed?
medicines_list <- 
  extracted_table %>%
  clean_names() %>%
  mutate(
    chapter = as.integer(str_extract(drug_class_name, pattern = "(?<=Chapter )\\d+"))
  ) %>%
  fill(chapter, .direction = "down") %>%  # complete blanks between chapters with the last non-blank chapter
  filter(bnf_subsection!="")  # remove chapters from the drug class column

zero_pad <- function(x) str_pad(string = x, width = 2, pad = "0")

test_list <-
  medicines_list %>%
  separate(col = bnf_subsection, into = paste0("c",1:4), sep = "\\.", remove = FALSE) %>%
  mutate(across(c1:c3, zero_pad)) %>%  # zero-pad digits except for 4th character, c4
  unite(col = "code", c1:c4, sep = "", na.rm = TRUE, remove = TRUE)
```

## Test against BNF to see if I get the same substances

Note: these need to be done in sections by how long the code given is - does it pick up a chapter, a section, a subsection, or specific medicines only?

```{r}
test_merge <-
  # test_list %>% 
  # select(drug_class_name, bnf_subsection, code) %>%
  # mutate(code = paste0("^",code)) %>%
  # regex_right_join(bnf, by = c("code"="bnf_chemical_substance_code"))
  bnf %>%
  regex_right_join(
    test_list %>%
      select(drug_class_name, bnf_subsection, code) %>%
      mutate(code = paste0("^",code)),
    by = c(bnf_chemical_substance_code = "code")
  )

# View(test_merge)

## what's left after matching all of the bnf to the provided codes?
test_merge2 <-
  bnf %>%
  regex_anti_join(
    test_list %>%
      select(drug_class_name, bnf_subsection, code) %>%
      mutate(code = paste0("^",code)),
    by = c(bnf_chemical_substance_code = "code")
  )
test_merge2 %>% count(bnf_section, bnf_section_code)
```
